A Tale of Two Dictionary Learning Problems

### 2020-08-05 manuscripts/thesis/results.tex
chapters

\section{Combinatorial designs for sparse supports}

@@

\section{Deterministic uniqueness theorems}

We are now in a position to state the main result, though for expository purposes the quantity $C_1$ will be left%(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
undefined until Sec.~\ref{DUT}. All results  below assume real matrices and vectors.

@@

\begin{corollary}\label{DeterministicUniquenessCorollary}
Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
\end{corollary}

@@

\section{Probabilistic uniqueness theorems}

>>>>

\section{Combinatorial designs}

@@

\section{Uniqueness Theorems}

\subsection{Deterministic Uniqueness Theorems}

We are now in a position to state the main result, though for expository purposes the quantity $C_1$ will be left%(a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) 
undefined until Chap.~\ref{DUT}.
 All results  below assume real matrices and vectors.

@@

\begin{corollary}\label{DeterministicUniquenessCorollary}
Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are \mbox{$N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$} vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ satisfying spark condition \eqref{SparkCondition} generates $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
\end{corollary}

@@

\subsection{Probabilistic uniqueness theorems}
